Reduced plasticity and opportunity for selection in terrestrial ectotherm populations under climate change

### 2023-03-29 ms.qmd
Landscape fig2

```{r}
#| label: fig-2
#| fig-cap: Acute and Acclimation lnRR q10 across traits for A) marine, B) freshwater and C) terrestrial systems
#| echo: false

@@

>>>>

\newpage
\begin{landscape}
```{r}
#| label: fig-2
#| fig-cap: Acute and Acclimation lnRR q10 across traits for A) marine, B) freshwater and C) terrestrial systems
#| echo: false

@@

\end{landscape}
